\resumeSubHeadingListStart


\resumeSubheading
    {Freelance}{Aug 2021 -- Present}
    {Software Engineer}{Remote}

    \resumeItemListStart
        \resumeItem{Developed and maintained over 10 projects across healthcare, e-commerce, real estate, and government services, ensuring user-centric and high-quality solutions.}
        \resumeItem{Led feature development, bug hunting, and post-deployment enhancements for projects such as DataHub, Demand Here, IDSDP, and FamilyTree, improving app stability and performance.}
        \resumeItem{Built and deployed the Moneybag Flutter package, a leading payment gateway in Bangladesh, integrating multiple payment methods and optimizing transaction workflows for security and user convenience.}
        \resumeItem{Fostered strong client relationships by delivering on-time solutions, maintaining clear communication, and providing ongoing support.}
    \resumeItemListEnd

\resumeSubheading
    {NDA (Part-time)}{Feb 2025 -- Present}
    {Flutter Developer}{}
    \resumeItemListStart
    \resumeItem{Refactored legacy Flutter codebase to improve performance and maintainability, while contributing new features to the production app at a London-based company.}
    \resumeItemListEnd
  

\resumeSubheading
    {Tincleo (Contract Role)}{Dec 2023 -- Nov 2024}
    {Flutter Developer}{Cameroon}

    \resumeItemListStart
        \resumeItem{Developed a cross-platform real estate app enabling seamless property transactions (renting and buying) with advanced search and filtering functionalities.}
        \resumeItem{Integrated dynamic features allowing users to request properties and property owners to post listings, enhancing user interaction and engagement.}
        \resumeItem{Ensured platform security by implementing user verification, scam alerts, and a review/rating system, providing a secure and trustworthy experience for all users.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
