%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart
   
\resumeProjectHeading
    {\href{https://github.com/yeasin50/read_me_when}{\textbf{Read me when}}} 
    {Dec 2024}
    \resumeItemListStart
    \resumeItem{Led and built an open-source app that displays Quranic verses for emotional and spiritual support.}
    \resumeItem{Added verse-sharing to help users connect and uplift each other.}
    \resumeItem{Designed a minimal, calming UI for a peaceful user experience.}
    \resumeItemListEnd
   
\resumeProjectHeading
    {\textbf{Locato} \  } 
    {Nov 2023}
    \resumeItemListStart
    \resumeItem{Refactored the entire Flutter codebase to boost performance and simplify future maintenance, enabling a smoother release cycle.}
    \resumeItem{Resolved critical bugs across the app to ensure a stable user experience during cross-border rental searches (US–France).}
    \resumeItem{Enhanced code readability and app structure, improving developer onboarding and collaboration efficiency.}
    \resumeItemListEnd
    
\resumeProjectHeading
    {\href{https://sites.google.com/view/diuresult/}{\textbf{DIU Result} }} 
    {Dec 2023}
    \resumeItemListStart
    \resumeItem{Developed the DIU Result app for Daffodil International University, automating mark-sheet retrieval and reducing a 3-day delay and 50 BDT fee.}
    \resumeItem{Implemented offline access and grade analysis features, enabling students to compare their performance with peers and make informed decisions.}
    \resumeItem{Introduced a course selection feature for retakes, further improving the app's value in enhancing the student experience and accessibility.}
    \resumeItemListEnd

\resumeSubHeadingListEnd